working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-25 Manuscript_draft/Manuscript_draft.Rmd
edits methods

 Moreover, Mantel test was also conducted between heterospecific pollen effect and   [Here I think you should think if this controls for the non independency of donors and recipients. I think not. Maybe look onto matrix regresions?). Moreover, pairwise evolutive distances were calculated with MEGA7 for two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL). The sequences of interest were downloaded from NCBI GenBank and the phylogenetic tree constructed by maximum likelihood with MEGA7.[Make a section on how you contrsucted phylogeny]().

To evaluate heterospecific pollen effect on seed production we performed linear mixed models. The distinct heterospecific pollination treatments were compared thorugh relevelling each variable with the cross pollination treatment which was our control for optimum seed production for all the species. The different replicates of each treatment were considered as random effects. The changes of seed production across species were compared through scaling the seed production with mean 0 and standard deviation of 1 prior to the analysis. All the analysis were conducted with the statistical language `R` `r citep(citation())`

In order to test the relative effect of traits on seed production with foreign pollen we performed mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (euclidean distances). Heterospecific pollen effect was considered as the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments. Moreover, to find a model with the best explanatory traits we used the function **bioenv** from R. Finally, we also conducted mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits.

We conducted mantel test to check for correlations between heterospecific pollen effect and phylogenetic distance.

the square root of the matrix of phylogenetic distance due to improvement in the statistical power (Letten & Cornwell 2014).

??We explored also the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect, the independent variable the different traits and the random effects the different treatments per species

>>>>

To evaluate heterospecific pollen effect on seed production we performed linear mixed models. The distinct heterospecific pollination treatments were compared thorugh relevelling each variable with the cross pollination treatment which was our control for optimum seed production for all the species. The different replicates of each treatment were considered as random effects. The changes of seed production across species were compared through scaling the seed production with mean 0 and standard deviation of 1 prior to the analysis. All the analysis were conducted with the statistical language `R` `r citep(citation())`.

In order to test the relative effect of traits on seed production with foreign pollen we performed mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (euclidean distances). Heterospecific pollen effect was considered as the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments. Moreover, to find a model with the best explanatory traits we used the function **bioenv** from R. Finally, we also conducted mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, We explored also the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect (develop this bit).

We conducted mantel test to check for correlations between heterospecific pollen effect and phylogenetic distance. Due to improvents in statistical power we used the square root of the phylogenetic distance (Letten & Cornwell 2014). Two different phylogenetic distances were used from two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL). The sequences were obtained from GenBank (https://www.ncbi.nlm.nih.gov/genbank/, accessed 20 Oct. 2018). The sequences were aligned with clustal omega and the pairwise evolutive distances were calculated with MEGA7.

### 2019-02-25 Manuscript_draft/Manuscript_draft.tex
edits methods

Moreover, Mantel test was also conducted between heterospecific pollen
effect and the square root of the matrix of phylogenetic distance due to
improvement in the statistical power (Letten \& Cornwell 2014).
\href{}{all is here, but I would break it by questions and give a bit
more detail, to avoid overwhelm the reader} We explored also the
relations between traits and heterospecific pollen effect through
generalized mixed models where the response variable was heterospecific
pollen effect, the independent variable the different traits and the
random effects the different treatments per species {[}Here I think you
should think if this controls for the non independency of donors and
recipients. I think not. Maybe look onto matrix regresions?). Moreover,
pairwise evolutive distances were calculated with MEGA7 for two kinds of
markers: 1) Internal transcribed spacer (ITS) and 2)
ribulose-bisphosphate carboxylase (RBCL). The sequences of interest were
downloaded from NCBI GenBank and the phylogenetic tree constructed by
maximum likelihood with MEGA7.\href{}{Make a section on how you
contrsucted phylogeny}.

To evaluate heterospecific pollen effect on seed production we performed
linear mixed models. The distinct heterospecific pollination treatments
were compared thorugh relevelling each variable with the cross
pollination treatment which was our control for optimum seed production
for all the species. The different replicates of each treatment were
considered as random effects. The changes of seed production across
species were compared through scaling the seed production with mean 0
and standard deviation of 1 prior to the analysis. All the analysis were
conducted with the statistical language \texttt{R} (R Core Team 2018)

In order to test the relative effect of traits on seed production with
foreign pollen we performed mantel test between the assymetrical matrix
of heterospecific pollen effect (10 by 10 matrix) with the different
distance matrices of traits (euclidean distances). Heterospecific pollen
effect was considered as the subtraction of seed production by hand
cross pollination minus seed production of the different heterospecific
pollen treatments.

The

>>>>

To evaluate heterospecific pollen effect on seed production we performed
linear mixed models. The distinct heterospecific pollination treatments
were compared thorugh relevelling each variable with the cross
pollination treatment which was our control for optimum seed production
for all the species. The different replicates of each treatment were
considered as random effects. The changes of seed production across
species were compared through scaling the seed production with mean 0
and standard deviation of 1 prior to the analysis. All the analysis were
conducted with the statistical language \texttt{R} (R Core Team 2018).

In order to test the relative effect of traits on seed production with
foreign pollen we performed mantel test between the assymetrical matrix
of heterospecific pollen effect (10 by 10 matrix) with the different
distance matrices of traits (euclidean distances). Heterospecific pollen
effect was considered as the subtraction of seed production by hand
cross pollination minus seed production of the different heterospecific
pollen treatments. Moreover, to find a model with the best explanatory
traits we used the function \textbf{bioenv} from R. Finally, we also
conducted mantel test between the matrix of heterospecific pollen effect
and the distance matrix from all the traits. Moreover, We explored also
the relations between traits and heterospecific pollen effect through
generalized mixed models where the response variable was heterospecific
pollen effect (develop this bit).

We conducted mantel test to check for correlations between
heterospecific pollen effect and phylogenetic distance. Due to
improvents in statistical power we used the square root of the
phylogenetic distance (Letten \& Cornwell 2014). Two different
phylogenetic distances were used from two kinds of markers: 1) Internal
transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase
(RBCL). The sequences were obtained from GenBank
(\url{https://www.ncbi.nlm.nih.gov/genbank/}, accessed 20 Oct. 2018).
The sequences were aligned with clustal omega and the pairwise evolutive
distances were calculated with MEGA7.
